---
title: "Vectors, Matricies and Systems of Equations"
author: "Gabriella Martinez"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    includes:
      in_header: header.html
    css: ./lab.css
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r}
install.packages("animation")
library(animation)
```

For this assignment, build the first letters for both your first and last name using point plots in R.  For example, the following code builds an H.

```{r builds an H}
par(mar=rep(4,4))

x=c(rep(0,500),seq(0,1,length.out=1000), rep(1,500))
y=c(seq(-1,1,length.out=500),rep(0,1000), seq(-1,1,length.out=500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))
```

```{r builds a G}
par(mar=rep(4,4))
y=c(rep(-1,500),seq(-1,1,length.out=1000), rep(1,500),seq(-1,0,length.out=1000), rep(0,500))
x=c(seq(-1,0,length.out=500),rep(-1,1000), 
    seq(-1,0,length.out=500), rep(0,1000),
    seq(-0.5,0, length.out=500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

```

Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation , and 4) projection in animated fashion.  
```{r}
a=diag(2)
x11()
for (i in seq(-3,3, length.out=50)){
  a[1,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[-1,-1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
#Shearing horizontally
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[1,2]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
#Shearing vertically
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[2,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
```



